\documentclass{article}

% Recommended packages for language encoding, fonts, and layout
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}

% Set the margins
\geometry{a4paper, margin=1in}

% Document metadata
\title{Software Requirements Specification (SRS)\\[1ex]\large for 'Dil Mange More' Food Delivery Web App}
\author{Your Team Name}
\date{\today}

\begin{document}

% Generates the title
\maketitle

% Table of Contents
\tableofcontents
\newpage

% 1 Introduction section
\section{Introduction}
\subsection{Purpose}
The purpose of this Software Requirements Specification (SRS) is to provide a comprehensive guide for the development of the 'Dil Mange More' food delivery web application using the MERN stack. It outlines the functional and non-functional requirements, design constraints, and other essential aspects to ensure a systematic and successful development process.

\subsection{Document Conventions}
Coding standards follow industry best practices, including the Airbnb JavaScript Style Guide for React.js components, ES6 syntax, and consistent naming conventions. In-code documentation is facilitated through the use of JSDoc for enhanced clarity and maintainability.

\subsection{Intended Audience and Reading Suggestions}
This document is intended for a diverse audience, including developers, testers, project managers, and stakeholders involved in the 'Dil Mange More' project. Developers can refer to the technical specifications, project managers can focus on the project scope, milestones, and potential challenges, while stakeholders can gain insights into the technical intricacies of the application.

\subsection{Project Scope}
The project scope encompasses the development of a user-friendly food delivery web application, 'Dil Mange More,' utilizing the MERN stack. Key components include a responsive React.js frontend, a scalable Node.js and Express.js backend, and MongoDB for efficient data storage. The scope also includes secure user authentication, real-time order processing, and integration with external payment gateways.

\subsection{References}
Refer to MongoDB Documentation \cite{mongodb-doc}, Express.js Documentation \cite{express-doc}, React.js Documentation \cite{react-doc}, and Node.js Documentation \cite{node-doc}.

% Overall Description section
\newpage
\section{Overall Description}
\subsection{Product Perspective}
The 'Dil Mange More' web app is a standalone system that interfaces with external payment gateways and utilizes external APIs for location and order tracking.

\subsection{Product Functions}
Major functions include user registration, food browsing, order placement, real-time order tracking, and payment processing.

\subsection{User Classes and Characteristics}
User classes include customers, administrators, and delivery personnel, each with distinct roles and permissions.

\subsection{Operating Environment}
The software will operate in a web browser environment and is compatible with major browsers (Chrome, Firefox, Safari).

\subsection{Design and Implementation Constraints}
Coding standards and compatibility with the MERN stack limit development options.

\subsection{User Documentation}
User documentation will include guides for registration, ordering, and tracking.

\subsection{Assumptions and Dependencies}
Assumptions include a stable internet connection for real-time tracking. Dependencies include external APIs for location services.

% External Interface Requirements section
\newpage
\section{External Interface Requirements}
\subsection{User Interfaces}
Logical characteristics of the user interface ensure an intuitive and responsive design.

\subsection{Hardware Interfaces}
The software interfaces with standard hardware components, relying on user devices for access.

\subsection{Software Interfaces}
The web app interfaces with external payment gateways and location APIs.

\subsection{Communications Interfaces}
Requirements include secure communication protocols for payment processing.

% System Features section
\newpage
\section{System Features}
\subsection{System Feature 1: User Authentication}
Secure user authentication using JWT for enhanced data privacy.

\subsection{System Feature 2: Real-time Order Processing}
Implementation of a real-time order processing system using WebSocket for instant updates.

% Repeat subsections as necessary for additional system features.

% Other Nonfunctional Requirements section
\newpage
\section{Nonfunctional Requirements}
\subsection{Performance Requirements}
Quantitative attributes include response time and throughput to ensure a seamless user experience.

\subsection{Safety Requirements}
Ensure the software mitigates possible harm, loss, or damage during use.

\subsection{Security Requirements}
Implement measures to protect against unauthorized access and ensure data security.

\subsection{Software Quality Attributes}
Additional quality characteristics include maintainability, scalability, and usability.

% Updation section
\newpage
\section{Updation}
\subsection{Software Update Requirements}
Define procedures and frequency for software updates.

\subsection{Data Migration and Updates}
Specify requirements for data migration, including strategies and timing.

\subsection{Document Update Process}
Detail the process for updating this SRS document, including version control and update frequency.

% References section
\newpage
\begin{thebibliography}{9}
    \bibitem{mongodb-doc}
    MongoDB Documentation,
    \url{https://docs.mongodb.com/}

    \bibitem{express-doc}
    Express.js Documentation,
    \url{https://expressjs.com/}

    \bibitem{react-doc}
    React.js Documentation,
    \url{https://reactjs.org/}

    \bibitem{node-doc}
    Node.js Documentation,
    \url{https://nodejs.org/en/docs/}
\end{thebibliography}

\end{document}
